Text as Policy: Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2016-02-08 manuscript/tables/ideology_regs.tex
ideology analysis only with sum scores now, paper updated

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Mon Dec 21 04:04:01 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Intercept & Estimate & Std.Dev & p.value \\ 
  \hline
Sum & 4.300 & -0.034 & 0.001 & 0.000 \\ 
  Mean & 3.814 & -0.025 & 0.001 & 0.000 \\ 
  Max & 3.972 & -0.031 & 0.001 & 0.000 \\ 
  No. Alignments & 0.486 & -0.009 & 0.001 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Log-Linear models for alignment and euclidian
distance in ideology. Two tailed p-values are generated from quadratic
assignment procedure with 1000 iterations. Std.Dev is the standard
deviation of the null distribution. The rows correspond to
different methods of aggregating the section alignments to bill
allignments: \textit{Sum}: Sum of alignment scores of all alignments,
\textit{Mean}: Average alignment score accross secion pairs bill dyad,
\textit{Max}: Highest alignment score seciton pairs of bill dyad,
\textit{No. Alignments}: Number of alignments for bill dyad.} 
\label{tab:ideology_regs}
\end{table}

>>>>

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Mon Feb  8 18:23:42 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Intercept & Estimate & Std.Dev & p \\ 
  \hline
1 & 4.300 & -0.034 & 0.001 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Log-Linear model for alignment and euclidian
distance in ideology. Two tailed p-values are generated from quadratic
assignment procedure with 1000 iterations. Std.Dev is the standard
deviation of the null distribution.} 
\label{tab:ideology_regs}
\end{table}

### 2016-02-08 manuscript/text_reuse.tex
fixed bug in ncsl - lid billmatching
ideology analysis only with sum scores now, paper updated

Condition a) is necessary, since some of the urls returned by the web query refer to blog entries or to protected websites that require NCSL membership. The rationale behind condition b) is to maximize the number of bills we can match to our database (see Figure \ref{fig:bill_desc}). We additionally constrain the number of bills per table to be below 100, in order to assure, that the topic of the table is not too broad. We chose 100 since this number would correspond roughly to two bills per state (often there is a house and a senate bill in each state for a particular policy).
The web query from step 1 returned 266 urls. From the 50 sampled urls 22 fulfilled the three criteria. From these 23 tables we constructed a dataset of 950 bills, of which we could match 581 to our bill database.

@@

In the following sections we present several analyses to assess this correlation. When we are generating the alignments the bills are split up into sections. Table \ref{tab:ideology_regs} displays results for several methods of combining multiple alignments across sections of the same bill dyad. Specifically we investigate four different ways of aggregating to the bill level: the sum of the alignment scores of the sections of a bill dyad, the mean of these scores, the maximum of the scores, and the number of alignments between two bills.

Each model is a log-linear model regressing the logarithm of the aggregated measure on the ideological distance between the ideal point of the two bills forming the dyad. The ideal point of the bill is derived from the ideal point of the bill sponsor. In cases where several legislators sponsor a bill we use the average of all sponsors' ideal points to obtain a single measure.

@@

The results in Table \ref{tab:ideology_regs} clearly show that there is a significant correlation between the ideological distance of the bills' sponsors and their text alignment score, regardless of the aggregation method. For each aggregation method, assuming the null hypothesis of no correlation, the probability for the observed estimate estimated as zero. This is also clear from Figure \ref{fig:qap_dist}, which shows histograms of the permutation distributions of the regression coefficients and the actual estimates as a red line.

@@

To asses the substantive importance of the effect size, Figure \ref{fig:ideo_interpret} displays the estimated decrease in mean alignment score when increasing the ideological distance of the bills. The vertical lines correspond to the ideological distances between the median democrat and republican, the 0.05 quantile and the 0.95 quantile of the total distribution of ideal points and the minimum and maximum of the total distribution. [FILL IN MORE INTERPRETATION WHEN NEW RESULTS ARE IN]

>>>>

Condition a) is necessary, since some of the urls returned by the web query refer to blog entries or to protected websites that require NCSL membership. The rationale behind condition b) is to maximize the number of bills we can match to our database (see Figure \ref{fig:bill_desc}). We additionally constrain the number of bills per table to be below 100, in order to assure, that the topic of the table is not too broad. We chose 100 since this number would correspond roughly to two bills per state (often there is a house and a senate bill in each state for a particular policy).
The web query from step 1 returned 266 urls. From the 50 sampled urls 22 fulfilled the three criteria. From these 22 tables we constructed a dataset of 950 bills, of which we could match 707 to our bill database.

@@

In the following sections we present several analyses to assess this correlation. When we are generating the alignments the bills are split up into sections. We generate an alignment score for a bill dyad by summing over all section dyads of the bill dyad.  Table \ref{tab:ideology_regs} displays regression results from a log-linear model regressing the logarithm of the bill dyad alignment score on the ideological distance between the ideal point of the two bills forming the dyad. The ideal point of the bill is derived from the ideal point of the bill sponsor. In cases where several legislators sponsor a bill we use the average of all sponsors' ideal points to obtain a single measure.

@@

The results in Table \ref{tab:ideology_regs} clearly show that there is a significant correlation between the ideological distance of the bills' sponsors and their text alignment score The null hypothesis of no correlation, the probability for the observed estimate estimated as zero. This is also clear from Figure \ref{fig:qap_dist}, which shows histograms of the permutation distributions of the regression coefficients and the actual estimates as a red line.

@@

To asses the substantive importance of the effect size, Figure \ref{fig:ideo_interpret} displays the estimated decrease in alignment score when increasing the ideological distance of the bills. The vertical lines correspond to the ideological distances between the median democrat and republican, the 0.05 quantile and the 0.95 quantile of the total distribution of ideal points and the minimum and maximum of the total distribution. [FILL IN MORE INTERPRETATION WHEN NEW RESULTS ARE IN]
